# did {.unnumbered}

::: small
R package for doubly-robust and ipw DiD estimator (callaway and sant'anna 2021)
:::

**did** is a package that implements the DiD estimators proposed by Callaway and Sant'Anna (2021) that solves the bias of the TWFE estimator in staggered DiD. Documentation can be found [here](https://bcallaway11.github.io/did/index.html).

Install the package as follows:

```{r}
#| eval: false

install.packages('did')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

# packages needed:
library(did)
library(readr)  # for importing data
df = read_csv('df.csv')
```

<br />

We use the `att_gt()` function to run the matching process of csdid:

::: small
Note: `id` variable should be transformed to an integer variable before starting. Set `cohort = 0` for never-treated units.
:::

```{r}
#| warning: false
#| message: false

mod = att_gt(
  # required arguments
  yname                   = "outcome",
  tname                   = "time",
  idname                  = "id",            # must be a integer-variable
  gname                   = "cohort",        # cohort = 0 for never-treated
  est_method              = "dr",            # change to ipw if you are having issues
  base_period             = "universal",     # do not change
  allow_unbalanced_panel  = T,               # generally good to keep this T
  data                    = df,
  xformla                 = ~ covar,        # (optional)
  control_group           = "nevertreated",  # use "notyettreated" if sample size is small
  panel                   = T                # change to F if you are using rep. cross-section
)
```

<br />

We use the `aggte()` function to aggregate our matched treatment effects into an overall treatment effect.

```{r}
#| comment: "#>"
#| class-output: r

mod |>
  aggte(type  = "simple", na.rm = T) |>
  summary(att)
```

<br />

We can estimate dynamic treatment effects with the `aggte()` function and plot with the `ggdid()` function.

```{r}
#| comment: "#>"
#| class-output: r
#| fig-height: 3.5
#| message: false
#| fig-align: center

mod |>
  aggte(type   = "dynamic", na.rm  = T) |>
  ggdid(
    xlab    = "Time to Treatment",  # x-axis label
    ylab    = "Dynamic ATT",        # y-axis label
    title   = "Dynamic Effects"     # you can include a title string if you want
  )
```

<br />

We can also aggregate effects by initial treatment period group, and with the `ggdid()` function:

```{r}
#| comment: "#>"
#| class-output: r
#| fig-height: 3
#| fig-align: center

mod |>
  aggte(type   = "group", na.rm  = T) |>
  ggdid(
    xlab    = "ATT Estimate",  # x-axis label
    ylab    = "Group",         # y-axis label
    title   = "Group ATT"      # you can include a title string if you want
  )
```
