# did2s {.unnumbered}

::: small
R package for 2-stage DiD estimator (Gardner 2021)
:::

**did2s** is a package that implements the 2-stage DiD estimator proposed by Gardner (2021) that solves the bias of the TWFE in staggered settings. Documentation can be found [here](https://kylebutts.github.io/did2s/index.html).

Install the package as follows:

```{r}
#| eval: false

install.packages('did2s')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(did2s)
library(ggfixest)  # for plotting
library(readr)  # for importing data
df = read_csv('df.csv')
```

<br />

We use the `did2s()` function to run the did2s estimation for the ATT.

::: small
The `first_stage =` should contain all covariates and fixed effects. If no covariates, the formula should be `~ 0 | id + time`. The `second_stage =` should only contain the treatment variable.
:::

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod = did2s(
  data          = df,
  yname         = "outcome",
  first_stage   = ~ covar | id + time,  # if no covar, see above
  second_stage  = ~ i(treat),
  treatment     = "treat",
  cluster_var   = "id"                  # clustered se var
)
mod |> summary()
```

The coefficient of `treat::1` is our estimate of the ATT - the causal effect of treatment on those who receive the treatment.

<br />

We still use the `did2s()` function to run the event study model, but we alter the second-stage of the model. We then use the `ggiplot()` function to plot our results.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r
#| fig-height: 4
#| fig-align: center

mod = did2s(
  data          = df,
  yname         = "outcome",
  first_stage   = ~ covar | id + time,             # if no covar, see notes
  second_stage  = ~ i(rel.time, ref = -1),  # see notes for group
  treatment     = "treat",
  cluster_var   = "id"                             # clustered se
)

mod |> ggiplot(
  xlab    = "Time Relative to Treatment",  # x-axis label
  ylab    = "Dynamic ATT Estimate",        # y-axis label
  main    = "Dynamic Treatment Effects",   # title for plot
) +
  xlim(-8, 8) # select how many periods to display

```
