# DIDmultiplegtDYN {.unnumbered}

::: small
R package for DIDmultiple estimator (de Chaisemartin and D'Haultfœuille 2024)
:::

**DIDmultiplegtDYN** is a package that implements the DIDmultiple estimator by de Chaisemartin and D'Haultfœuille (2024), that solves the issues with TWFE, handles non-absorbing and continuous treatments. Documentation can be found [here](https://cran.r-project.org/web/packages/DIDmultiplegtDYN/DIDmultiplegtDYN.pdf).

Install the package as follows:

```{r}
#| eval: false

install.packages('DIDmultiplegtDYN')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(DIDmultiplegtDYN)
library(ggplot2)  # for plotting
library(readr)    # for importing data
df = read_csv('df.csv')
```

<br />

We use the `did_multiplegt_dyn()` function to complete the estimation process.

::: small
If you have a continuous or quasi-continuous treatment, or are having issues, set `continuous = 1`. Covariates for conditional parallel trends are possible to include, but they are used differently, and may cause issues.
:::

```{r}
#| comment: "#>"
#| class-output: r
#| message: false
#| warning: false

mod = did_multiplegt_dyn(
  # required arguments
  df          = df,
  outcome     = "outcome",
  group       = "id",       # Note: group here refers to unit, not cohort
  time        = "time",
  treatment   = "treat",
  effects     = 4,          # Number of post-treatment periods dynamic effects
  placebo     = 4,          # Number of pre-treatment periods of effects
  controls    = NULL,       # optional, vector (string) of covariates.
  continuous  = NULL,       # change to 1 if your treatment is true
  graph_off   = T
)

mod |> print()
```

The `Estimation of treatment effects: Event-study effects` are the post-treatment dynamic effects. The `Average cumulative (total) effect per treatment unit` is the ATT estimate. The `Testing the parallel trends and no anticipation assumptions` is the pre-treatment coefficient estimates.

<br />

We can plot the dynamic treatment effects in a plot. The simplest way is to use the default plot - in the original model estimation within `did_multiplegt_dyn()`, set `graph_off =` equal to `F`.

However, the default plot is kind of ugly (in my opinion), and also does not use the conventional numbering of the initial treatment period (it uses t=1 as the initial treatment period). Thus, we can also manually create a ggplot:

```{r}
#| message: false
#| warning: false
#| fig-height: 4
#| fig-align: center

# extract effects (the rev() function used because placebo effects are in the opposite order)
effects = c(rev(mod$results$Placebos[,1]), 0, mod$results$Effects[,1])  # extract pre/post effects
lwr = c(rev(mod$results$Placebos[,3]), 0, mod$results$Effects[,3])  # extract lower confint
upr = c(rev(mod$results$Placebos[,4]), 0, mod$results$Effects[,4]) # extract upper confint

# create rel.time variable matching number of pre/post periods
rel.time = c(-5:3)

# create plotting dataframe
plot.df = data.frame(rel.time, effects, lwr, upr)

# ggplot
plot.df |>
  ggplot(aes(x = rel.time, y = effects)) +
  geom_point() +
  geom_linerange(aes(ymin = lwr, ymax = upr)) +
  geom_hline(yintercept = 0, color = "gray") +
  geom_vline(xintercept = -0.5, color = "gray") +
  labs(title = "Event-Study Estimates (DIDmultipleDYN)") +
  xlab("Time to initial treatment period") +
  ylab("Estimate") +
  theme_light()
```
