# DIDmultiple

##### De Chaisemartin and D'Haultfœuille (2020, 2024)

### What is DIDmultiple?

The DIDMultiple estimator, also called **csdid**, is an estimator for DiD that solves the issues with TWFE in staggered settings. It also expands DiD to work with continuous treatments and non-absorbing treatments. The estimator was proposed by de Chaisemartin and D'Haultfœuille (2020, 2024).

DIDmultiple is a **matching and reweighting estimator** for DiD, with the matching part solving the "forbidden comparisons" problem of TWFE, and the reweighting part solving the "negative weighting" problem of TWFE.

The estimator focuses on **switchers** - those units in a certain period who change their treatment status. For example, a unit that goes from $D_{it} = 0$ to $D_{it} = 1$. DIDmultiple "matches" these switchers to the group that does not switch (so the group of units that stay $D_{it} = 0$), and estimates the difference in outcomes. In a binary treatment setting, the treatment effect at period $\tau_t$ can be described as:

$$
\tau_t = \frac{\mathbb E[\Delta Y |\text{switchers}] - \mathbb E[\Delta Y |\text{non-switchers}]}{\underbrace{\mathbb E[\Delta D |\text{switchers}]}_\text{=1 if absorbing treatment}}
$$

::: small
This might seem similar to those familar with IV-wald estimator, and in fact, this is a Wald estimator, called Wald-TC.
:::

Then, DIDmultiple aggregates these effects of switchers by reweighting them properly. This can be used to estimate both a singular ATT and dynamic effects. The focus on switchers allows DIDmultiple to be applied onto non-binary treatments, including continuous treatments.

<br />

### R: Running the Model

```{r}
#| echo: false
#| warning: false
#| message: false

library(fixest)
data(base_stagg, package = "fixest")
df <- base_stagg
colnames(df) <- c("unit", "time", "cohort", "rel.time", "treated", "te", "covar", "outcome")
df$treat <- ifelse(df$rel.time >= 0, 1, 0)
```

Our dataset `df` should be a panel or repeated cross-section, and have the following variables:

| Variable  | Description                                                                                                                         |
|-----------|-------------------------------------------------------------------------------------------------------------------------------------|
| `unit`    | A variable indicating the units/individual an observation belongs to in our data.\* [For csdid, this must be integers]{.underline}. |
| `time`    | A variable indicating time-periods in our study for each observation.                                                               |
| `outcome` | Outcome variable for each observation.                                                                                              |
| `covar`   | (optional) covariate(s) to condition for parallel trends.                                                                           |

::: small
\*For repeated cross-section, the `unit` variable should be instead the group/level of which treatment is assigned. For example, if treatment is assigned by county/state, use that as the `unit` variable.
:::

With all the proper variables, we can estimate a DIDmultiple model with the **DIDmultiplegtDYN** package:

```{r}
library(DIDmultiplegtDYN)

DIDmultiple <- did_multiplegt_dyn(
  df = df,
  outcome    = "outcome",
  group      = "unit",    # Note: group here refers to unit, not first.treat
  time       = "time",
  treatment  = "treat",
  controls   = NULL,      # optional, vector of covariates. I have difficulties.
  effects    = 4,         # Number of post-treatment periods dynamic effects
  placebo    = 4,         # Number of pre-treatment periods of effects
  continuous = NULL,      # change to 1 if your treatment is true
  graph_off  = T
)
```

The model has now been run, and we can now output the effects or plot the effects.

<br />

### R: Output the Effects

We can output the effects from a DIDmultiple model as follows:

```{r}
#| warning: false
#| message: false
#| comment: "#>"
#| class-output: r

print(DIDmultiple)
```

This output contains quite a lot of material.

1.  The first section are dynamic treatment effects for post-treatment periods.
2.  The second section is the average cumulative effect per treatment unit, also equivalent to the ATT in a binary setting.
3.  The final section contains pre-treatment effects, which can help us determine if parallel trends is met. The joint-nullity test of the placebos should be non-significant if parallel trends is met.

::: {.callout-note collapse="true" appearance="simple"}
## Extracting ATT Estimates

We can extract the ATT directly for plots or figures with the following:

```{r}
#| comment: "#>"
#| class-output: r
#| results: hold

# ATE
DIDmultiple$results$ATE[1]

# Standard Error
DIDmultiple$results$ATE[2]

# Lower confidence interval
DIDmultiple$results$ATE[3]

# Upper confidence interval
DIDmultiple$results$ATE[4]
```
:::

<br />

### R: Plotting Dynamic Effects

The DIDmultiple model automatically generates a ggplot. We can make a few modifications to the plot:

```{r}
#| eval: false

library(ggplot2)

# assign plot to plot object
plot <- DIDmultiple$plot

# get rid of weird line in degault plot
plot$layers[[1]] <- NULL

# customise plot
plot +
  # title and axis-labels
  labs(title = "Dynamic Treatment Effects") +
  xlab("Time to Treatment (t=1)") + ylab("Estimate") +
  
  # lines for treatment time and 0 treatment effect
  geom_vline(xintercept = 0.5, linetype = 3) +
  geom_hline(yintercept = 0, linetype = 3, color = "red") +
  
  # Theme
  theme_bw()

```

```{r}
#| echo: false
#| message: false
#| fig-height: 3
#| fig-align: center

library(ggdark)
library(ggplot2)

# assign plot to plot object
plot <- DIDmultiple$plot

# get rid of weird line in degault plot
plot$layers[[1]] <- NULL

# customise plot
plot +
  # title and axis-labels
  labs(title = "Dynamic Treatment Effects") +
  xlab("Time to Treatment (t=1)") + ylab("Estimate") +
  
  # lines for treatment time and 0 treatment effect
  geom_vline(xintercept = 0.5, linetype = 3) +
  geom_hline(yintercept = 0, linetype = 3, color = "red") +
  
  # Theme
  dark_mode(theme_bw())
  
```

<br />

### Additional Resources

de Chaisemartin, C. and D'Haultfœuille, X (2024) 'Difference-in-Differences Estimators of Intertemporal Treatment Effects', *The Review of Economics and Statistics*, pp. 1-45. Available at: <https://doi.org/10.1162/rest_a_01414>.

de Chaisemartin, C. and D'Haultfœuille, X (2020) 'Two-Way Fixed Effects Estimators with Heterogenous Treatment Effects', *American Economic Review*, 110(9), pp. 2964-2996. Available at: <https://www.nber.org/system/files/working_papers/w25904/w25904.pdf>.

*Additional Links*:

-   Asjad Naqvi's [page on DIDmultipleDYN](https://asjadnaqvi.github.io/DiD/docs/code_r/07_did_multiplegt_dyn_r/).
-   Yiqing Xu's [section on DIDmultiple](https://asjadnaqvi.github.io/DiD/docs/code_r/07_did_multiplegt_dyn_r/).
-   DIDmultiplegtDYN [package documentation](https://cran.r-project.org/web/packages/DIDmultiplegtDYN/DIDmultiplegtDYN.pdf).
