# DIDmultiplegtDYN {.unnumbered}

::: small
non-staggered or staggered, absorbing or non-absorbing, binary or continuous treatment
:::

The DIDMultiple estimator is an estimator for DiD that solves the issues with TWFE in staggered settings. It also expands DiD to work with continuous treatments and non-absorbing treatments.

The estimator focuses on **switchers** - those units in a certain period who change their treatment status. In a binary treatment setting, the treatment effect at period $\tau_t$ can be described as:

$$
\tau_t = \frac{\mathbb E[\Delta Y |\text{switchers}] - \mathbb E[\Delta Y |\text{non-switchers}]}{\underbrace{\mathbb E[\Delta D |\text{switchers}]}_\text{=1 if absorbing treatment}}
$$

::: small
For example, a unit that goes from $D_{it} = 0$ to $D_{it} = 1$. DIDmultiple "matches" these switchers to the group that does not switch (so the group of units that stay $D_{it} = 0$), and estimates the difference in outcomes.
:::

Then, DIDmultiple aggregates these effects into a singular ATT or dynamic effects. The focus on switchers allows DIDmultiple to be applied onto non-binary treatments, including continuous treatments.

```{r}
#| message: false
#| warning: false

# packages needed:
library(DIDmultiplegtDYN)
```

<br />

```{r}
#| echo: false
#| warning: false
#| message: false

library(fixest)
data(base_stagg, package = "fixest")
df <- base_stagg
colnames(df) <- c("id", "time", "cohort", "rel.time", "treated", "te", "covar", "outcome")
df$treat <- ifelse(df$rel.time >= 0, 1, 0)
```

::: panel-tabset
## Syntax

We use the `did_multiplegt_dyn()` function to complete the estimation process:

```{r}
m1 = did_multiplegt_dyn(
  # required arguments
  df          = df,
  outcome     = "outcome",
  group       = "id",       # Note: group here refers to unit, not first.treat
  time        = "time",
  treatment   = "treat",
  effects     = 4,          # Number of post-treatment periods dynamic effects
  placebo     = 4,          # Number of pre-treatment periods of effects
  
  # optional arguments
  controls    = NULL,       # optional, vector (string) of covariates.
  continuous  = NULL,       # change to 1 if your treatment is true
  graph_off   = T
)
```

## Variables

Our dataset `df` should be a panel or repeated cross-section, and have the following variables:

| Variable  | Description                                                                         |
|-----------------|------------------------------------------------------|
| `id`      | A variable indicating the units/individual an observation belongs to in our data.\* |
| `time`    | A variable indicating time-periods in our study for each observation.               |
| `outcome` | Outcome variable for each observation.                                              |
| `covar`   | (optional) covariate(s) to condition for parallel trends.                           |

::: small
\*For repeated cross-section, the `unit` variable should be instead the group/level of which treatment is assigned. For example, if treatment is assigned by county/state, use that as the `unit` variable.
:::

## Notes

Covariates for conditional parallel trends are possible to include, but they are used differently, and may cause issues.
:::

<br />

Our results can be outputted into print form, or into a plot:

::: panel-tabset
## Print

We can print the results from our object from previously:

```{r}
#| warning: false
#| message: false
#| comment: "#>"
#| class-output: r

m1 |> print()
```

## Plot

We can plot the dynamic treatment effects in a plot:

```{r}
#| message: false
#| warning: false
#| fig-height: 3
#| fig-align: center

library(ggplot2)

# assign plot to plot object
plot = m1$plot

# get rid of weird line in default plot
plot$layers[[1]] <- NULL

# customise plot
plot +
  labs(title = "Dynamic Treatment Effects") +
  xlab("Time to Treatment (t=1)") + ylab("Estimate") +
  
  # lines for treatment time and 0 treatment effect
  geom_vline(xintercept = 0.5, linetype = 3) +
  geom_hline(yintercept = 0, linetype = 3, color = "red") +
  
  # Theme
  theme_bw()
```
:::

<br />

**Additional Resources**

de Chaisemartin, C. and D'Haultfœuille, X (2024) 'Difference-in-Differences Estimators of Intertemporal Treatment Effects', *The Review of Economics and Statistics*, pp. 1-45. Available at: <https://doi.org/10.1162/rest_a_01414>.

de Chaisemartin, C. and D'Haultfœuille, X (2020) 'Two-Way Fixed Effects Estimators with Heterogenous Treatment Effects', *American Economic Review*, 110(9), pp. 2964-2996. Available at: <https://www.nber.org/system/files/working_papers/w25904/w25904.pdf>.

*Additional Links*:

-   Asjad Naqvi's [page on DIDmultipleDYN](https://asjadnaqvi.github.io/DiD/docs/code_r/07_did_multiplegt_dyn_r/).
-   Yiqing Xu's [section on DIDmultiple](https://asjadnaqvi.github.io/DiD/docs/code_r/07_did_multiplegt_dyn_r/).
-   DIDmultiplegtDYN [package documentation](https://cran.r-project.org/web/packages/DIDmultiplegtDYN/DIDmultiplegtDYN.pdf).
