# etwfe {.unnumbered}

::: small
R package for extended-twfe (Wooldridge 2021, 2023)
:::

**etwfe** is a package that implements the extended twfe estimator proposed by Wooldridge (2021, 2023) that solves the bias of the TWFE in staggered settings. Documentation can be found [here](https://grantmcdermott.com/etwfe/index.html).

Install the package as follows:

```{r}
#| eval: false

install.packages('etwfe')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(etwfe)
library(readr)  # for importing data
df = read_csv('df.csv')
```

<br />

We use the `etwfe()` function to estimate the etwfe model:

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod = etwfe(
  fml     = outcome ~ covar,  # see notes for no covar
  tvar    = time,
  gvar    = cohort,
  data    = df,
  vcov    = ~ id,
  family  = NULL              # can change to "logit", "negbin", "poisson"
)
```

<br />

We can use the `emfx()` function to aggregate our heterogenous effects into a singular ATT.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod |> emfx(type = "simple")
```

The `estimate` for `TRUE` is our ATT, and the p-value is given by `Pr(>|Z|)`.

<br />

We can use the `emfx()` function to aggregate dynamic treatment effects. We can then plot these effects with the `plot()` function. Note that etwfe cannot estimate pre-treatment effects.

```{r}
#| message: false
#| warning: false
#| fig-height: 4
#| fig-align: center

mod |>
  emfx(type = "event") |>
  plot()
```

If we are interested in how the ATT differs by year of treatment adoption, we can also aggregate effects by initial treatment period group. We can then plot these effects with the `plot()` function:

```{r}
#| message: false
#| warning: false
#| fig-height: 4
#| fig-align: center

mod |>
  emfx(type = "group") |>
  plot()
```

<br />
