# fect {.unnumbered}

::: small
R package for imputation estimators FEct, IFEct, and MC (Liu et al 2024)
:::

**fect** is a package that implements imputation DiD estimators proposed by Liu, Xu, and Wang (2024) that solves the bias of the TWFE estimator in staggered and non-absorbing DiD. **fect** also includes modern estimators (ifect, mc) that are semi-robust against parallel trends violations. Documentation can be found [here](https://yiqingxu.org/packages/fect/02-fect.html).

Install the package as follows:

```{r}
#| eval: false

install.packages('fect')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(fect)
library(readr)  # for importing data
df = read_csv('df.csv')
```

<br />

Use the `fect()` function to estimate models. To switch between the models, alter the `method =` argument.

::: small
You should generally start with fect, then see if parallel trends is met, before going to ifect and mc. If you use ifect and mc, set `CV = T`.
:::

```{r}
#| comment: "#>"
#| class-output: r
#| message: false
#| warning: false

mod = fect(
  formula  = outcome ~ treat + covar,  # covar is optional
  data     = df,
  index    = c("id", "time"),          # unit and time var
  method   = "fe",                     # use "fe", "ife", or "mc"
  CV       = F,                        # change to T for "ife" or "mc"
  se       = T,                        # don't change
  nboots   = 40,                       # usually you should use 200, larger is slower
  seed     = 1239                      # any number will work
)

mod |> print()
```

The output contains two different ATT estimates. It is typically conventional to use the first one, `Tr obs equally weighted`, which weights each observation $it$ equally (rather than the second which weights all $i$ equally).

<br />

To plot dynamic effects, we use the `plot()` function.

```{r}
#| message: false
#| fig-height: 4
#| fig-align: center

mod |> plot(
  start0  = T,                    # don't change
  main    = NULL,                 # title
  ylab    = "Estimate",           # y-axis label
  xlab    = "Time to Treatment",  # x-axis label
  xlim    = c(-7, 7)              # what time periods to include (offset by +1)
)
```

We can also plot the distributions of dynamic treatment effects as follows:

```{r}
#| message: false
#| fig-height: 4.5
#| fig-align: center

mod |> plot(
  start0  = T,                    # don't change
  type    = "box",                # don't change
  main    = NULL,                 # title
  ylab    = "Estimate",           # y-axis label
  xlab    = "Time to Treatment",  # x-axis label
  xlim    = c(-7, 7)              # what time periods to include (offset by +1)
)
```

The fect package contains an F-test and equivalence test to test parallel trends, accessed through `plot()`:

```{r}
#| message: false
#| fig-height: 4.5
#| fig-align: center

mod |> plot(
  start0      = T,                    # don't change
  type        = "equiv",
  bound       = "equiv",
  pre.period  = c(-4, 0),             # how many pre-treat coef to test
  main        = NULL,                 # title
  ylab        = "Estimate",           # y-axis label
  xlab        = "Time to Treatment",  # x-axis label
  xlim        = c(-7, 7)              # what time periods to include (offset by +1)
)
```

::: small
An F-test tests if the joint combination of pre-treatment coefficients is statistically significantly different than 0. Since we do not want the coefficients to be different than 0, we want to get a high p-value and fail to reject the null.

An Equivalence (TOST) test tests if the confidence intervals of our pre-treatment coefficients are within 0.36 standard deviations of the outcome variable of 0. Essentially, it tests if there is a substantively significant deviation in parallel trends.
:::
