# fixest {.unnumbered}

::: small
R package for TWFE and Interaction-Weighted (Sun and Abraham 2021)
:::

**fixest** (and companion **ggfixest**) is a package for regressions targeted toward econometrics. For DiD, fixest allows the implementation of a basic TWFE model, as well as the Sun and Abraham (2021) interaction-weighted estimator. Documentation can be found [here](https://lrberge.github.io/fixest/).

Install the package as follows:

```{r}
#| eval: false

install.packages('fixest')
install.packages('ggfixest')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(fixest)
library(ggfixest)
library(readr)  # for importing data
df = read_csv('df.csv')
```

<br />

We use the `feols()` function to run the TWFE model.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod = feols(
  fml   = outcome ~ treat + covar | id + time,  # covar is optional
  data  = df,                                   # your data
  vcov  = ~ id                                  # cluster SE by unit
)
mod |> summary()
```

<br />

We use the `feols()` function to run the TWFE event study for dynamic treatment effects.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r
#| fig-height: 3
#| fig-align: center

mod = feols(
  fml   = outcome ~ i(rel.time, group, ref = -1) + covar | id + time,  # group = treat/never-treat
  data  = df,                                                          # your data
  vcov  = ~ id                                                         # cluster SE by unit
)
mod |> ggiplot(
  xlab    = "Time Relative to Treatment",  # x-axis label
  ylab    = "Dynamic ATT Estimate",        # y-axis label
  main    = "Dynamic Treatment Effects",   # title for plot
) +
  xlim(-8, 8) # select how many periods to display
```

We add the `sunab()` function within `feols()` to implement the staggered DiD "Interaction-Weighted" estimator proposed by Sun and Abraham (2020).

::: small
Note: The `cohort` value for never-treated units should be a very large or very small number outside of the range of `time`.
:::

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r
#| fig-height: 3
#| fig-align: center

mod = feols(
  fml = outcome ~ sunab(cohort, time) + covar | id + time,  # covar is optional
  data = df,
  vcov = ~ id                                               # clusters se by unit (id)
)
mod |>
  aggregate(agg  = "att") |>  # agg can also be "group" or "dynamic"
  print()
```

<br />

And we can plot the Sun and Abraham event study using the `ggiplot()` function.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r
#| fig-height: 3
#| fig-align: center

mod |> ggiplot(
  xlab    = "Time Relative to Treatment",       # x-axis label
  ylab    = "Dynamic ATT Estimate",             # y-axis label
  main    = "Dynamic Treatment Effects (IW)",   # title for plot
) + 
  xlim(-8, 8)                                   # how many periods to include.
```
