# didimputation {.unnumbered}

::: small
R package for the imputation estimator (Borusyak et al 2021)
:::

**didimputation** is a package that implements the imputation DiD estimator proposed by Borusyak, Jaravel, and Speiss (2021) that solves the issues with TWFE in staggered settings. Documentation can be found [here](https://github.com/kylebutts/didimputation).

Install the package as follows:

```{r}
#| eval: false

install.packages('didimputation')
```

------------------------------------------------------------------------

#### sample code

Start by loading packages and the data:

```{r}
#| message: false
#| warning: false

library(didimputation)
library(ggplot2)  # for plotting
library(readr)    # for importing data
df = read_csv('df.csv')
```

<br />

We use the `did_imputation()` function to run the model.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod = did_imputation(
  data         = df,
  yname        = "outcome",
  gname        = "cohort",
  tname        = "time",
  idname       = "id",
  first_stage  = ~ covar | id + time  # can delete entire arg if no covars
)

mod |> print()
```

<br />

We can also estimate event-study dynamic effects for pre and post-treatment periods.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

mod = did_imputation(
  data         = df,
  yname        = "outcome",
  gname        = "cohort",
  tname        = "time",
  idname       = "id",
  first_stage  = ~ covar | id + time,  # can delete entire arg if no covars
  horizon = T,                         # do not change
  pretrends = -4:-1                    # how many pre-treatment period to include
)
```

There is no simple built-in plot function for the package, so we will need to manually create a ggplot.

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r
#| fig-height: 4
#| fig-align: center


# convert output into table
tbl = mod |> as.data.table()

# filter for only treatment coefficients
tbl$term = tbl$term |> as.numeric()
tbl = tbl |> na.omit()

# ggplot
tbl |>
  ggplot(aes(x = term, y = estimate)) +
  geom_vline(xintercept = -0.5, color = "gray") +
  geom_hline(yintercept = 0, color = "gray") +
  geom_point() +
  geom_linerange(aes(ymin = conf.low, ymax = conf.high)) + 
  labs(title = "Dynamic Treatment Effects") +
  xlab("Time to Treatment") +
  ylab("Estimate") +
  theme_light()
```
