---
title: "Two-Way Fixed Effects"
---

### What is TWFE?

Two-way fixed effects (TWFE) is the primary estimator used to estimate causal effects in difference-in-differences. The TWFE estimator is a regression model specified as follows:

$$
Y_{it} = \underbrace{\alpha_i + \gamma_t}_\text{fixed effects} + D_{it}\tau + \cov + \eps_{it}
$$

The variables in this regression model are:

-   $Y_{it}$ is our outcome variable value for unit $i$ at time $t$.
-   $D_{it}$ is our treatment variable value (treated = 1, not treated = 0) for unit $i$ at time $t$.
-   $\mathbf X_{it}$ is a vector of covariate variable values for unit $i$ at time $t$. These covariates are optional, and are used if we believe they are needed to meet the parallel trends assumption.

Fixed effect $\alpha_i$ accounts/controls for differences between units, and $\gamma_t$ accounts/controls for differences between time periods.

If we account for differences between units and differences between time periods, the only possible confounders remaining are unit-specific trends over time. But with the parallel trends assumption, we rule out this type of confounder.

Thus, under the parallel trends assumption, there are no omitted confounders/variables, and our regression is exogenous. Since OLS is unbiased under exogeneity, our TWFE estimator for $\tau$ is unbiased.

There are [issues with TWFE] that you should understand before relying on TWFE.

<br />

### R: Estimating the ATT

```{r}
#| echo: false
#| warning: false
#| message: false

library(fixest)
data(base_stagg, package = "fixest")
df <- base_stagg
colnames(df) <- c("unit", "time", "cohort", "rel.time", "treat", "te", "covariate", "outcome")
```

Our dataset `df` should have the following variables:

-   `unit`: variable indicating units $i$ in our dataset.
-   `time`: variable indicating the time-periods $t$ in our dataset.
-   `treat`: variable indicating the treatment status of unit $i$ at time-period $t$. Should equal 1 if treated, and 0 if not treated.
-   `outcome`: variable indicating the outcome value of unit $i$ at time-period $t$.

We can also have these optional variables:

-   `covariate`: a control variable (if needed) to meet parallel trends. We can have multiple.

We then use the **feols()** command to run a TWFE model:

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

library(fixest)

att <- feols(
  fml   = outcome ~ treat + covariate | unit + time,  # covariate is optional
  data  = df,                                         # your data
  vcov  = ~unit                                       # cluster SE by unit
)

summary(att)
```

The coefficient of `treat` is our estimate of the ATT - the causal effect of treatment on those who receive the treatment. The significance is given by `Pr(>|t|)` (the p-value) and the stars `***` .

<br />

### R: Estimating Dynamic Effects

We can also estimate dynamic treatment effects with the TWFE estimator. Our dataset `df` should have the following variables:

-   `unit`: variable indicating units $i$ in our dataset.
-   `time`: variable indicating the time-periods $t$ in our dataset.
-   `outcome`: variable indicating the outcome value of unit $i$ at time-period $t$.
-   `rel.time`: a relative time variable that indicates for period $t$, how many periods away unit $i$ first received treatment (0 is the year they received treatment, negatives are before treatment, positives after treatment). For info on how to create this variable, see the appendix.

We can also have these optional variables:

-   `covariate`: a control variable (if needed) to meet parallel trends. We can have multiple.

We then use the **feols()** command to run a TWFE model for dynamic effects:

```{r}
#| message: false
#| warning: false
#| comment: "#>"
#| class-output: r

library(fixest)

dynamic <- feols(
  # Formula
  fml   = outcome ~ i(rel.time, ref = c(-1, Inf)) + covariate | unit + time,
  # Do not change -1 in c(). You change Inf to the value of never-treated for rel.time
  
  data  = df,     # your data
  vcov  = ~unit   # cluster SE by unit
)

head(coeftable(dynamic))  # head because this table is long
```

The output here contains the dynamic effects from rel.time periods -20 to -15. You can see more of them if you get rid of the `head()` function surrounding the `coeftable(dynamic)`.

These results aren't too useful on their own. It is much more useful to plot these results.

```{r}
#| eval: false

library(ggfixest)
library(ggplot2)

plot <- ggiplot(
  # required options
  object   = dynamic,           # input your dynamic model name
  drop     = "[[:digit:]]{2}",  # this limits pre-post period to -9 to 9.
  ref.line = FALSE,             # we will add our own line later
  
  # optional aesthetic options
  xlab     = "Time Relative to Treatment",  # x-axis label
  ylab     = "Dynamic ATT Estimate",        # y-axis label
  main     = "Dynamic Treatment Effects",   # title for plot
)

plot +
  geom_vline(xintercept = -0.5, linetype = 3) +               # add treatment begin line
  geom_hline(yintercept = 0, linetype = 3, color = "red")     # add 0 effect line
# ggfixest allows us to add any additional ggplot2 options
```

```{r}
#| message: false
#| warning: false
#| fig-height: 3
#| echo: false

library(ggdark)
library(ggfixest)

plot <- ggiplot(
  # required options
  object   = dynamic,           # input your dynamic model name
  drop     = "[[:digit:]]{2}",  # this limits pre-post period to -9 to 9.
  ref.line = FALSE,             # we will add our own line later
  
  # optional aesthetic options
  xlab     = "Time Relative to Treatment",  # x-axis label
  ylab     = "Dynamic ATT Estimate",        # y-axis label
  main     = "Dynamic Treatment Effects",   # title for plot
)

plot +
  geom_vline(xintercept = -0.5, linetype = 3) +               # add treatment begin line
  geom_hline(yintercept = 0, linetype = 3, color = "red") +  # add 0 effect line
  dark_mode(theme_bw())

```

Here we can see all of our dynamic treatment effects plotted. We can split the dynamic treatment effects into 2 groups for interpretation purposes.

1.  Pre-treatment (before the white dotted line). If parallel trends assumption is met, then the confidence intervals of the estimates should cover 0 (the red line).

::: small
In this example, we can see evidence that parallel trends is violated.
:::

2.  Post-treatment (after the white dotted line). These coefficients represent the treatment effect over time. If their confidence intervals do not include 0, that means the treatment effect is significant.

::: small
In this example, we can see the initial post-treatment periods have negative effects, but this becomes positive as the years go on.
:::

<br />

### Issues with TWFE

TWFE has been shown to be a **biased** estimator (bad estimator) for the ATT and dynamic treatment effects when dealing with staggered treatment implementation. So when units begin treatment at different times, TWFE is biased.

Why is this? Goodman-Bacon (2021) shows that in a staggered setting, TWFE is actually a weighted average of 4 comparisons:

1.  Early-treated units vs. untreated units.
2.  Late-treated units vs. untreated units.
3.  Early-treated units vs. late-treated units before treatment.
4.  Early-treated units after treatment vs. late-treated units before **and** **after** treatment.

When we compare treatment to control, we want to compare treated to untreated units. The issue comes with the 4th comparison - we actually use late-treated units **after** receiving treatment as a untreated comparison. This is called the "forbidden comparison" problem of TWFE.

De Chaisemartin and D'Haultœuille (2020) show that there is another problem with TWFE - the weighting of these comparisons when aggregating these comparisons. For an accurate **average treatment effect** on the treated (ATT), we in theory want to weight each comparison by the proportion of the sample size each comparison contains. For example, if more units are in the early-treated units, we would want to weight that comparison more.

The issue with TWFE is that not only does it not weight by group size, it doesn't even always give positive weights. In fact, sometimes, TWFE will assign **negative** weights to certain comparisons. This is completely nonsensical, and has been shown to even **reverse** the sign of the true ATT in simulations.

Thus, TWFE is a **biased** estimator [when it comes to staggered treatment]{.underline} designs. Since 2021, Econometricians have started developing **modern estimators** that resolve the issues with TWFE.

<br />

<br />

### When to Use TWFE?

We have established that TWFE is a **biased** estimator [when it comes to staggered treatment]{.underline} designs. Thus, we should be cautious when using TWFE in these situations.

The general advice is to not rely on TWFE if there is any staggered treatment implementation or non-absorbing treatment.

However, while we cannot rely on TWFE, it is still very conventional to estimate a TWFE model and report the results. While in theory TWFE can be very biased (as explained above), in reality, it often is not that different than any other modern estimators.
